\thispagestyle{empty}
\subsection*{\huge Black Mage}
\vspace{0.3cm}
"You sure are a keen observer of the obvious, kupo!" \\
\indent -- Montblanc 
\vspace{0.3cm} \\
Black magic is a pathway to many abilities some consider to be unnatural. 
Black Mages are fragile in physical combat, but can wipe out multiple enemies from great distances and inflict nasty status effects. 
They can thus assert great control over the battlefield and are difficult to ignore for enemies. \\
\vfill
\battrt
{
	\textbf{Level 1:} & HP~+17 & MP~+21 & AGI~+2 & MAG~+1  \\
	\textbf{Level 2:} & HP~+5  & MP~+10 & STR~+1 & RES~+1  \\
	\textbf{Level 3:} & HP~+10 & MP~+10 & MAG~+1 &         
}
{Staff}
{Robe}
\vfill
\atypet{Arcanist}
{
	\textbf{Level 4:} & HP~+5  & MP~+5  & MAG~+2 & DEF~+1 \\ 
	\textbf{Level 5:} & HP~+5  & MP~+10 & RES~+1 & MAG~+1 \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & RES~+1 & DEF~+1 \\
	\textbf{Level 7:} & HP~+10 & MP~+10 & MAG~+1 &  	  \\
	\textbf{Level 8:} & HP~+5  & MP~+10 & MAG~+1 & DEF~+1 \\
	\textbf{Level 9:} & HP~+10 & MP~+5  & RES~+1 & MAG~+1 \\
	\textbf{Level 10:}& HP~+5  & MP~+10 & RES~+2 &		  
}
{Magic Boost}
{	
	Whenever you cast \hyperlink{action}{Magic} that targets a single entity, you can choose to also target everyone within 1u of him. The damage dealt to secondary targets is halved.
}
{Critical Vanish}
{	
	Whenever you have more than 1 HP and an \hyperlink{action}{Attack} would reduce you to 0 HP, you remain at 1 HP and gain \hyperlink{status}{Blink} for 3 rounds or until you take an action.
}
\vfill
\atypet{Scholar}
{	
	\textbf{Level 4:} & MP~+10 & RES~+1 & DEF~+1 & MAG~+1 \\
	\textbf{Level 5:} & HP~+10 & MP~+10 & MAG~+1 		  \\
	\textbf{Level 6:} & HP~+5  & MP~+10 & RES~+1 & MAG~+1 \\
	\textbf{Level 7:} & HP~+5  & MP~+10 & MAG~+2  		  \\
	\textbf{Level 8:} & HP~+5  & MP~+10 & RES~+1 & DEF~+1 \\
	\textbf{Level 9:} & HP~+5  & MP~+10 & RES~+1 & MAG~+1  \\
	\textbf{Level 10:}& HP~+10 & MP~+10 & MAG~+1		  \\
}
{Turbo MP}
{	
	Whenever you begin casting \hyperlink{action}{Magic}, you can choose to double its range by also doubling the MP cost.
}
{Return Magic}
{	
	Whenever you suffer damage caused by \hyperlink{action}{Magic}, you can cast the same spell back to its caster.
	In doing this, you have to respect the cast time and MP cost of the spell.
	If you are already casting another spell, you have to break its concentration to use this effect. 
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\spellt{Fire}{4}{1r}{Single}{3u}
{
	You deal 2d \hyperlink{type}{fire} damage to the target.
}{\fire}{1}
\spellt{Blizzard}{4}{1r}{Single}{3u}
{
	You deal 2d \hyperlink{type}{ice} damage to the target.
}{\ice}{1}
\spellt{Thunder}{4}{1r}{Single}{3u}
{
	You deal 2d \hyperlink{type}{lightning} damage to the target.
}{\lightning}{1}
\spellt{Blind}{6}{1r}{Single}{3u}
{
	The target makes a DC 8 check and suffers \hyperlink{status}{Blind} for 3 rounds upon failure.
}{\blind}{2}
\spellt{Bio}{8}{1r}{Single}{3u}
{
	The target makes a DC 8 check and suffers 2d damage and \hyperlink{status}{Poison} for 3 rounds upon failure.
}{\poison}{3}
\spellt{Firaga}{12}{2r}{Single}{5u}
{
	You deal 6d \hyperlink{type}{fire} damage to the target. 
}{\fire}{5}
\spellt{Blizzaga}{12}{2r}{Single}{5u}
{
	You deal 6d \hyperlink{type}{ice} damage to the target. 
}{\ice}{5}
\spellt{Thundaga}{12}{2r}{Single}{5u}
{
	You deal 6d \hyperlink{type}{lightning} damage to the target. 
}{\lightning}{5}
\spellt{Rasp}{4}{1r}{Single}{5u}
{
	You reduce the target's MP by 4d.
}{}{6}
\spellt{Quake}{22}{2r}{3u}{8u}
{
	Deal 8d \hyperlink{type}{earth} damage to everyone in the target area. 
}{\earth}{7}
\spellt{Flare}{24}{3r}{Single}{5u}
{
	You deal 9d+15 \hyperlink{type}{fire} damage to the target. 
}{\fire}{8}
\spellt{Doom}{28}{1r}{Single}{5u}
{
	The target makes a DC 8 check and suffers \hyperlink{status}{KO} after 3 rounds upon failure.
}{\ko}{9}
\spellt{Ultima}{40}{3r}{3u}{5u}
{
	Deal 10d+20 \hyperlink{type}{dark} damage to all enemies in the target area. 
}{\dark}{10}
\pagebreak