\thispagestyle{empty}
\subsection*{\huge Dragoon}
\vspace{0.3cm}
"Confident bastard, aren't you?" \\
\indent -- Kain 
\vspace{0.3cm} \\
Dragoons are masters of aerial combat, that strike their enemies with devastating attacks from the sky.
They prefer spears as their weapon and have an affinity for the fire element. 
Even though they are humanoid, it is said that Dragoons have the soul of a dragon inside them.
\vfill
\battrt
{
	\textbf{Level 1:} & HP +23 & MP~+11 & AGI~+2,& STR~+1 \\
	\textbf{Level 2:} & HP~+5  & MP~+5 & STR~+1 & RES~+2 \\
	\textbf{Level 3:} & HP~+10 & MP~+5 & STR~+1 & DEF~+1 \\
}
{Spear}{Heavy Armor}
\vfill
\atypet{Dragon Knight}
{	
	\textbf{Level 4:} & HP~+5  & MP~+10 & RES~+2 &	   	  \\
	\textbf{Level 5:} & HP~+10 & MP~+10 & STR~+1 & 		  \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & DEF~+1 & RES~+1 \\
	\textbf{Level 7:} & HP~+10 & MP~+5  & STR~+2 & 	  	  \\ 
	\textbf{Level 8:} & HP~+10 & MP~+10 & RES~+1 & 	 	  \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & DEF~+1 & STR~+1 \\ 
	\textbf{Level 10:}& HP~+5  & RES~+2 & DEF~+2 \\
}
{Flametongue}
{	You gain permanent \hyperlink{type}{resilience} against \hyperlink{type}{fire} damage.
	Furthermore, whenever you deal damage by leaping on an enemy from above, you can choose to let the damage dealt be of \hyperlink{type}{magical} and \hyperlink{type}{fire} type.
}
{Dragonheart}
{	
	Whenever you deal or receive \hyperlink{type}{fire} damage, you gain \hyperlink{status}{EnSTR} until the end of your next turn.
}
\vfill
\atypet{Valkyrie}
{
	\textbf{Level 4:} & HP~+5  & MP~+10 & DEF~+2 &  	  \\
	\textbf{Level 5:} & HP~+10 & MP~+10 & RES~+1 &  	  \\ 
	\textbf{Level 6:} & HP~+10 & MP~+5  & STR~+1 & RES~+1 \\
	\textbf{Level 7:} & HP~+5  & MP~+5  & STR~+2 & DEF~+1 \\
	\textbf{Level 8:} & HP~+10 & MP~+5  & DEF~+1 & RES~+1 \\
	\textbf{Level 9:} & HP~+5  & MP~+10 & STR~+2 &	      \\
	\textbf{Level 10:}& HP~+10 & MP~+5  & DEF~+1 & RES~+1 \\
}
{Duelist}
{
	As long as you are in combat with one enemy and there are no other allies or enemies within 3u of you, you gain \hyperlink{status}{Blink}.
}
{Final Attack}
{	Whenever you receive damage that would cause to suffer \hyperlink{status}{KO}, you can immediately use one of your abilities without any cast time before falling unconscious.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\techt{Jump}{3}{1r}{Single}{3u}
{
	When you begin using this \hyperlink{action}{Tech}, you jump 3u up into the air.
	After the cast time is up, you leap onto the target and make an \hyperlink{action}{Attack} on him.
}{}{1}
\techt{Lancet}{3}{1r}{Single}{3u}
{
	You reduce the target's HP and MP by 1d and increase your HP and MP by the same amount.
}{}{2}
\techt{Fire Breath}{7}{0r}{3u (front)}{Self}
{
	You deal 4d \hyperlink{type}{fire} damage to everyone in the target area.
}{\fire}{3}
\techt{Double Jump}{9}{1r}{Single}{4u}
{
	When you begin using this tech, you jump 3u up into the air.
	After the cast time is up, you leap onto the target and make an \hyperlink{action}{Attack} on him.
	You can then leap to another location within 3u.
	If you land on another enemy you can make an \hyperlink{action}{Attack} on him too.
}{}{5}
\techt{Full Thrust}{7}{0r}{5u (line)}{Self}
{
	You dash forward in a up to 5u long line.
	Make an \hyperlink{action}{Attack} on everyone in the way by making one damage roll that is applied to all targets that fail to evade.
}{}{6}
\techt{Roar}{8}{0r}{3u}{Self}
{
	Everyone within the target area makes a DC 9 check and suffers \hyperlink{status}{Immobile} for 1 round upon failure.
}{\immobile}{7}
\techt{Revenge}{12}{0r}{Single}{Weapon}
{
	Make an \hyperlink{action}{Attack} on an enemy that has damaged you in the last round. 
	On hit, you inflict the damage that he dealt to you before, on top of the usual damage.
}{}{8}
\techt{Dragon Dive}{16}{2r}{3u}{5u}
{
	When you begin using this \hyperlink{action}{Tech} you jump 3u up into the air.
	After the cast time is up you leap on the target and deal 7d \hyperlink{type}{fire} damage to everyone in the target area except yourself.
}{\fire}{9}
\techt{Highwind}{26}{0r}{Single}{Weapon}
{
	You make an \hyperlink{action}{Attack} on the target that is guaranteed to hit and then jump 4u up into the air. 
	The target is launched 3u into the air as well for 1 round.
	At the beginning of your next turn, you dive downwards, striking the target into the ground and scoring a \hyperlink{action}{Critical Hit} on him.
}{}{10}
\pagebreak