\thispagestyle{empty}
\subsection*{\huge Marksman}
\vspace{0.3cm}
"I play the leading man; who else?" \\
\indent -- Balthier 
\vspace{0.3cm} \\
Marksmen are experts of all kinds of ranged weapons that strike from great distance. 
Skilled Marksmen can see through their enemies, allowing them to know target's strengths and weaknesses. 
Therefore they can not only deal significant ranged damage, but also disable enemies with special techniques. 
For the Marksman there is but one rule: hunt or be hunted.
\vfill
\battrt
{
	\textbf{Level 1:} & HP +19 & MP~+12 & AGI~+2 & STR +1 \\
	\textbf{Level 2:} & HP~+5  & MP~+10 & STR~+1 & DEF~+1 \\
	\textbf{Level 3:} & HP~+10 & MP~+5  & STR~+1 & RES~+1 \\
}{Bow, Gun}{Light Armor}
\vfill
\atypet{Ranger}
{	
	\textbf{Level 4:} & HP~+10 & MP~+10 & STR~+1 &        \\
	\textbf{Level 5:} & HP~+5  & MP~+10 & DEF~+2 &        \\
	\textbf{Level 6:} & HP~+10 & MP~+10 & RES~+1 &        \\
	\textbf{Level 7:} & HP~+5  & MP~+10 & STR~+1 & RES~+1 \\
	\textbf{Level 8:} & HP~+5  & MP~+5  & RES~+1 & DEF~+2 \\
	\textbf{Level 9:} & HP~+5  & MP~+10 & RES~+1 & STR~+1 \\
	\textbf{Level 10:}& HP~+10 & MP~+5  & STR~+2 &        \\
}
{Recoil}
{	
	Whenever you make a successful \hyperlink{action}{Attack}, you can immediately move 1u even when wielding a bow.
}
{Magic Evade}
{	
	You can evade \hyperlink{action}{Magic} by passing an evasion check, the same way you evade \hyperlink{action}{Attacks}.
}
\vfill
\atypet{Sniper}
{	
	\textbf{Level 4:} & HP~+5  & MP~+5  & STR~+2 & RES~+1 \\
	\textbf{Level 5:} & HP~+10 & MP~+10 & DEF~+1 &		  \\
	\textbf{Level 6:} & HP~+5  & MP~+10 & STR~+1 & DEF~+1 \\
	\textbf{Level 7:} & HP~+5  & MP~+5  & STR~+1 & RES~+2 \\
	\textbf{Level 8:} & HP~+5  & MP~+10 & DEF~+1 & RES~+1 \\
	\textbf{Level 9:} & HP~+10 & MP~+5  & STR~+2 &        \\
	\textbf{Level 10:}& HP~+5  & MP~+5  & RES~+1 & STR~+2 \\
}
{Concentrate}
{	
	Whenever you \hyperlink{action}{Attack} an enemy, he has \hyperlink{check}{Disadvantage} on the evasion check.
}
{Auto-Item}
{	
	Whenever you suffer any damage, you can immediately use an \hyperlink{item}{Item}.
	You can only use this effect once per round.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
	\techt{Big Shot}{3}{0r}{Single}{Weapon}
	{
		Make an \hyperlink{action}{Attack} on the target. 
		If you hit, the damage dealt ignores the target's DEF.
	}{}{1}
	\techt{Lay Trap}{4}{1r}{1u}{Self}{
		You set a trap where you are standing.
		An enemy that walks over it makes a DC 9 check and suffers 2d damage and \hyperlink{status}{Immobile} for 1 round upon failure.
		The trap disappears once it is activated.
	}{\immobile}{2}
	\spellt{Libra}{5}{0r}{Single}{3u}
	{
		You analyse the target thoroughly and know his \hyperlink{type}{Resiliences}, \hyperlink{type}{Weaknesses}, \hyperlink{type}{Immunities}, as well as his current HP and MP.
	}{}{3}
	\techt{Quick Shot}{9}{0r}{Single}{Weapon}
	{
		You make an \hyperlink{action}{Attack} after which you can immediately begin using an \hyperlink{action}{Ability} or \hyperlink{item}{Item} on the same turn.
	}{}{5}
	\techt{Pierceshot}{7}{0r}{10u (line)}{Self}
	{
		You make an \hyperlink{action}{Attack} against all targets in a line, by making one damage roll that applies to everyone that fails to evade.	
	}{}{6}
	\techt{Poison Ammo}{8}{0r}{Single}{Weapon}
	{
		Make an \hyperlink{action}{Attack} on the target. 
		If you hit, the damage dealt is \hyperlink{type}{magical} and the target makes a DC 8 check. 
		Upon failure, he suffers \hyperlink{status}{Poison} for 3 rounds.	
	}{\poison}{7}
	\techt{Target MP}{4}{1r}{Single}{Weapon}
	{
		Make an \hyperlink{action}{Attack} on the target.
		If you hit, you reduce his MP by the amount of damage dealt instead of his HP.
	}{}{8}
	\techt{Smoke Bomb}{12}{1r}{3u}{5u}
	{
		You create a smoke cloud that inhibits vision in the target area for 5 rounds.
		Everyone inside the cloud suffers \hyperlink{status}{Blind}, but gains \hyperlink{status}{Blink}.
	}{\blind\blink}{9}
	\techt{Barrage}{22}{1r}{Single}{Self}
	{
		For up to 3 rounds you make 2 consecutive \hyperlink{action}{Attacks} as your action on every turn.
		As long as this effect is active, you cannot move or take other actions.
		You can choose to end this effect at the start of every turn.
	}{}{10}
\pagebreak
