\thispagestyle{empty}
\subsection*{\huge Monk}
\vspace{0.3cm}
"Now I know why I have these stupid muscles!" \\
\indent -- Sabin 
\vspace{0.3cm} \\
Monks are adept melee fighters that posses a deadly combination of strength and technique.
While they do not have expertise in using magic, Monks can produce similarly incredible effects by tapping into their inner life force. 
A skilled monk absorbs what is useful, discards what is useless and adds what is specifically his own.
\vfill
\battrt
{
	\textbf{Level 1:} & HP +22 & MP~+10  & AGI~+4 & \\
	\textbf{Level 2:} & HP~+10 & MP~+5  & STR~+2 & \\
	\textbf{Level 3:} & HP~+10 & MP~+10 & DEF~+1 & \\
}{Claw}{Light Armor}
\vfill
\atypet{Black Belt}
{		
	\textbf{Level 4:} & HP~+10 & MP~+5  & STR~+2 &        \\ 
	\textbf{Level 5:} & HP~+5  & MP~+10 & DEF~+1 & RES~+1 \\
	\textbf{Level 6:} & HP~+10 & MP~+5  & STR~+1 & RES~+1 \\
	\textbf{Level 7:} & HP~+10 & MP~+5  & STR~+1 & DEF~+1 \\ 
	\textbf{Level 8:} & HP~+10 & MP~+5  & STR~+2 &        \\
	\textbf{Level 9:} & HP~+5  & MP~+10 & STR~+1 & RES~+1 \\ 
	\textbf{Level 10:}& HP~+10 & MP~+10 & STR~+1 &        \\ 
}
{Unscarred}
{	
	As long as your current HP is equal to your maximum HP, the STR bonus that is added to the damage dealt by your \hyperlink{action}{Attacks} is doubled.
}
{Strikeback}
{	
		Whenever you successfully evade an \hyperlink{action}{Attack} by an enemy, immediately make an \hyperlink{action}{Attack} on him.
}
\vfill
\atypet{Templar}
{	
	\textbf{Level 4:} & HP~+5  & MP~+10 & STR~+1 & RES~+1 \\ 
	\textbf{Level 5:} & HP~+10 & MP~+5  & DEF~+2 & 		  \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & STR~+2 & 		  \\ 
	\textbf{Level 7:} & HP~+10 & MP~+5  & RES~+2 & 	      \\ 
	\textbf{Level 8:} & HP~+10 & MP~+10 & STR~+1 & 	      \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & RES~+1 & STR~+1 \\ 
	\textbf{Level 10:}& HP~+10 & MP~+10 & STR~+1 & 		  \\ 
}
{Lifestream}
{	
	If you do not have enough MP to use an ability you can instead choose to reduce your HP by the amount of its MP cost in order to use it.
}
{Replenish MP}
{	
	Whenever you suffer \hyperlink{type}{physical} damage, increase your MP by 1d.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\techt{Boost}{3}{0r}{Single}{Self}
{
	You gain \hyperlink{status}{EnSTR} until the end of your next turn. 
}{\enstr}{1}
\techt{Chakra}{6}{1r}{Single}{Self}
{
	You regain 1d HP and remove all \hyperlink{status}{Status Effects} that you are currently suffering.
}{}{2}
\techt{Kick}{8}{0r}{1u}{Self}
{
	You make an \hyperlink{action}{Attack} against all enemies within 1u of you, by making one damage roll that applies to all affected targets that fail to evade. All targets that fail to evade are also knocked back by 1u. 
}{}{3}
\techt{Pummel}{9}{0r}{Single}{Weapon}
{
	You make 2 consecutive \hyperlink{action}{Attacks} against the target. 
}{}{5}
\techt{Vigilance}{6}{0r}{Single}{Self}
{
	You gain \hyperlink{status}{Blink} until the end of your next turn. 
}{\blink}{6}
\techt{Revive}{16}{3r}{Single}{1u}
{
	You remove \hyperlink{status}{KO} from the target and increase his HP by~1. 
}{\ko}{6}
\techt{Aurablast}{7}{0r}{Single}{3u}
{
	You deal 4d \hyperlink{type}{magical} damage to the target.
}{}{7}
\techt{Meteor Strike}{16}{0r}{Single}{Weapon}
{
	You slam the target into the ground dealing 7d damage.
	In doing this, you can also leap to a location of your choice within 3u.
}{}{8}
\techt{Blitz}{5}{0r}{Single}{Self}
{
	You use two different \hyperlink{action}{Techs} consecutively in the same turn.
	In doing this, you have to respect additional MP costs and cast times of both \hyperlink{action}{Techs}.
	If an enemy is affected by both \hyperlink{action}{Techs}, deal an additional 4d damage to him.
}{}{9}
\techt{Final Heaven}{24}{0r}{Single}{Weapon}
{
	You deal 6d damage to the target and knock him back by 3u.
	If he hits a wall or a similarly solid object in doing so, you deal another 4d damage to him.
}{}{10}
\pagebreak