\thispagestyle{empty}
\subsection*{\huge Red Mage}
\vspace{0.3cm}
"Oh, I’ll show you how lightning strikes." \\
\indent -- Lightning 
\vspace{0.3cm} \\
Red Mages are very versatile characters, that possess a wide variety of abilities. 
They are capable of using offensive and defensive spells, but can also
hold their own in melee combat. 
Although they excel in neither discipline, their incredible flexibility
and speed makes Red Mages a force to be reckoned with.
\vfill
\battrt
{
	\textbf{Level 1:} & HP~+20 & MP~+16 & AGI~+3 & STR +1 \\
	\textbf{Level 2:} & HP~+5  & MP~+10 & MAG~+1 & DEF~+1 \\
	\textbf{Level 3:} & HP~+10 & MP~+5  & RES~+2 &        \\
}{Staff, Sword}{Light Armor, Robe}
\vfill
\atypet{Ravager}
{	
	\textbf{Level 4:} & HP~+5  & MP~+10 & MAG~+1 & RES~+1 \\ 
	\textbf{Level 5:} & HP~+10 & MP~+5  & STR~+2 &        \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & MAG~+2 &        \\ 
	\textbf{Level 7:} & HP~+10 & MP~+5  & STR~+1 & DEF~+1 \\ 
	\textbf{Level 8:} & HP~+5  & MP~+10 & STR~+1 & MAG~+1 \\ 
	\textbf{Level 9:} & HP~+10 & MP~+10 & RES~+1 &        \\ 
	\textbf{Level 10:}& HP~+5  & MP~+10 & MAG~+1 & DEF~+1 \\ 
}
{Overwhelm}
{	
	Whenever you inflict damage to an enemy that you have already damaged within the previous round, your damage dealt ignores the target's DEF and RES.
}
{Swiftcast}
{	
	Whenever you suffer damage while not concentrating, you can immediately use an ability without cast time.
	You can only use this effect once per round.
}
\vfill
\atypet{Spellblade}
{		
	\textbf{Level 4:} & HP~+10 & MP~+5  & STR~+1 & DEF~+1 \\ 
	\textbf{Level 5:} & HP~+5  & MP~+10 & MAG~+2 & 		  \\ 
	\textbf{Level 6:} & HP~+10 & MP~+5  & STR~+2 &		  \\ 
	\textbf{Level 7:} & HP~+5  & MP~+10 & DEF~+1 & STR~+1 \\ 
	\textbf{Level 8:} & HP~+10 & MP~+5  & STR~+1 & MAG~+1 \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & DEF~+1 & RES~+1 \\ 
	\textbf{Level 10:}& HP~+10 & MP~+10 & STR~+1 		  \\ 
}
{Magic Weapon}
{	
	Whenever you cast \hyperlink{action}{Magic}, you can choose to store the spell inside your weapon.
	If you do this, the spell costs only half as much MP as usual.
	The spell then takes effect on the next target that you hit with an \hyperlink{action}{Attack} on top of your usual damage.
	You cannot store more than one spell at once inside your weapon.
}
{Mana Shield}
{	
	Whenever your HP is reduced, you can instead choose to reduce your MP by the same amount.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\spellt{Cure}{4}{1r}{Single}{3u}
{
	The target regains 2d HP. 
}{}{1}
\spellt{Poison}{6}{1r}{Single}{3u}
{
	The target makes a DC 8 check and suffers \hyperlink{status}{Poison} for 3 rounds upon failure.
}{\poison}{2}
\spellt{Fira}{8}{1r}{Single}{4u}
{
	You deal 4d \hyperlink{type}{fire} damage to the target.
}{\fire}{3}
\spellt{Blizzara}{8}{1r}{Single}{4u}
{
	You deal 4d \hyperlink{type}{ice} damage to the target.
}{\ice}{3}
\spellt{Thundara}{8}{1r}{Single}{4u}
{
	You deal 4d \hyperlink{type}{lightning} damage to the target.
}{\lightning}{3}
\spellt{Silence}{6}{1r}{Single}{3u}
{
	The target makes a DC 8 check and suffers \hyperlink{status}{Silence} for 3 rounds upon failure.
}{\silence}{5}
\spellt{Esuna}{6}{1r}{Single}{3u}
{
	You remove all \hyperlink{status}{Status Effects} except \hyperlink{status}{KO} from the target.
}{}{6}
\techt{Elemental Strike}{4}{0r}{Single}{Weapon}
{
	Choose an \hyperlink{type}{element} (e.g. \hyperlink{type}{fire}) and make an \hyperlink{action}{Attack}. 
	If you hit, the damage is of \hyperlink{type}{magical} type with the chosen element. 
}{}{7}
\spellt{Wall}{10}{1r}{Single}{3u}
{
	The target gains \hyperlink{status}{EnDEF} and \hyperlink{status}{EnRES} for 3 rounds.
}{\enndef \enres}{8}
\spellt{Imperil}{10}{1r}{Single}{3u}
{
	The target suffers \hyperlink{status}{DeDEF} and \hyperlink{status}{DeRES} for 3 rounds.
}{\dedef \deres}{8}
\spellt{NulElement}{12}{1r}{Single}{5u}
{
	Choose an \hyperlink{type}{element} (e.g. \hyperlink{type}{fire}). 
	The target does not suffer any damage of the chosen element for 3 rounds.
}{}{9}
\spellt{Dualcast}{4}{0r}{Single}{Self}
{
	You begin casting and concentrating on two spells of your choice simultaneously, but need to spend the necessary MP for both.
}{}{10}
\pagebreak