\thispagestyle{empty}
\subsection*{\huge Sentinel}
\vspace{0.3cm}
"Allow me to shatter your delusions of grandeur." \\
\indent -- Beatrix 
\vspace{0.3cm} \\
Sentinels are masters of defensive combat that will rarely fall in a battle.  
Their special abilities allow them to not only withstand incredible amounts of damage, but also provide protection to their allies.
A capable Sentinel is often the last thing standing between the party and certain death.
\vfill
\battrt
{
\textbf{Level 1:} & HP~+28 & MP~+13 & AGI~+3 & DEF~+1  \\
\textbf{Level 2:} & HP~+10 & MP~+10 & STR~+1 & RES~+1 \\
\textbf{Level 3:} & HP~+10 & MP~+10 & DEF~+1 &  
}{Sword}{Heavy Armor}
\vfill
\atypet{Defender}
{		
	\textbf{Level 4:} &  HP~+10 & MP~+5  &  DEF~+1 & STR~+1 \\ 
	\textbf{Level 5:} &  HP~+10 & MP~+5  &  STR~+1 & DEF~+1	\\ 
	\textbf{Level 6:} &  HP~+10 & MP~+10 &  RES~+1 &        \\ 
	\textbf{Level 7:} &  HP~+10 & MP~+5  &  STR~+1 & DEF~+1 \\
	\textbf{Level 8:} &  HP~+10 & MP~+5  &  RES~+1 & DEF~+1 \\
	\textbf{Level 9:} &  HP~+10 & MP~+5  &  DEF~+2 & 		\\ 
	\textbf{Level 10:}&  HP~+10 & MP~+5  &  STR~+2 &        \\
}
{Provoke}
{	
	Whenever you successfully \hyperlink{action}{Attack} an enemy, you can try to provoke him.
	If you do so, he has to make a DC~7 check and upon failure he has to target you with an action on his next turn if possible.
}
{Block}
{	
	Whenever an enemy within 1u of you tries to move away from you, he has make a DC 7 check.
	Upon failure, he suffers \hyperlink{status}{Immobile} until the start of his next turn, preventing him from moving any further on this turn.
}
\vfill
\atypet{Paladin}
{	
	\textbf{Level 4:} & HP~+10 & MP~+10 & DEF~+1          \\
	\textbf{Level 5:} & HP~+10 & MP~+5  & RES~+1 & DEF~+1 \\ 
	\textbf{Level 6:} & HP~+10 & MP~+5  & STR +2 &        \\
	\textbf{Level 7:} & HP~+10 & MP~+5  & RES +2 &        \\
	\textbf{Level 8:} & HP~+10 & MP~+5  & STR +1 & DEF~+1 \\
	\textbf{Level 9:} & HP~+10 & MP~+10 & STR +1 &        \\
	\textbf{Level 10:}& HP~+5  & MP~+10 & RES~+1 & DEF +1 \\
}
{Holy Guard}
{	
	As long as there is an ally within 1u of you, both of you gain \hyperlink{status}{Blink}.
	This benefit cannot apply to more than one ally at once.
}
{Cover}
{	
	Whenever an ally within 1u of you receives \hyperlink{type}{physical} damage, you can decide to direct half of the total damage dealt on yourself instead of onto your ally.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\techt{Guard}{3}{0r}{Single}{Self}{
	You gain \hyperlink{status}{EnDEF} until the end of your next turn. 
}{\enndef}{1}
\techt{First Aid}{5}{0r}{Single}{1u}{
	Choose a target that has received damage within one round, including yourself. The target regains 2d HP. 
}{}{2}
\techt{Powerbreak}{10}{0r}{Single}{Weapon}{
	Make an \hyperlink{action}{Attack} against the target. 
	If you hit, he suffers \hyperlink{status}{DeSTR} and \hyperlink{status}{DeMAG} for 3 rounds on top of the damage dealt. 
}{\destr \demag}{3}
\techt{Mediguard}{9}{1r}{Single}{Self}{
	You gain \hyperlink{status}{EnDEF} for 3 rounds and when this effect ends, you regain 2d HP. 
}{\enndef}{5}
\spellt{Earth Wall}{10}{1r}{3u (line)}{3u}{
	You create a 3u tall and wide wall of earth that blocks the path.
	The wall breaks down after 5 rounds or upon suffering a total of 30 damage.
}{}{6}
\techt{Threaten}{8}{1r}{Single}{3u}{
	The target makes a DC 8 check and suffers \hyperlink{status}{Immobile} for 3 rounds upon failure.
}{\immobile}{7}
\spellt{Astra}{11}{1r}{Single}{3u}{
	For the next 3 rounds, the target becomes \hyperlink{status}{Immune} to all \hyperlink{status}{Status Effects}.
}{}{8}
\techt{Mow Down}{16}{0r}{Single}{Weapon}{
	Make an \hyperlink{action}{Attack} against the target. 
	If you hit, the target suffers the difference between your current and your maximum HP instead of your usual damage. 
}{}{9}
\techt{Omniguard}{30}{1r}{Single}{Self}{
	For the next 3 rounds, you cannot suffer any damage.
}{}{10}
\pagebreak
