\thispagestyle{empty}
\subsection*{\huge Thief}
\vspace{0.3cm}
"I PREFER the term ”treasure hunter!" \\
\indent -- Locke 
\vspace{0.3cm} \\
Thieves are extremely mobile melee fighters, who can quickly traverse the battlefield and are difficult
to hit with physical attacks. 
They excel at "borrowing" items and money from enemies and have a heightened sense for worthwhile business. 
One would be advised to be careful when dealing with a Thief, they always have one more trick up their
sleeve than you would expect.
\vfill
\battrt
{
	\textbf{Level 1:} & HP +20 & MP~+14 & AGI~+4 &        \\
	\textbf{Level 2:} & HP~+5  & MP~+5  & STR~+2 & DEF~+1 \\
	\textbf{Level 3:} & HP~+10 & MP~+10 & RES~+1 &        \\
}{Dagger}{Light Armor}
\vfill
\atypet{Assassin}
{	
	\textbf{Level 4:} & HP~+10 & MP~+5  & STR~+1 & DEF~+1 \\ 
	\textbf{Level 5:} & HP~+10 & MP~+10 & STR~+1 &        \\ 
	\textbf{Level 6:} & HP~+5  & MP~+5  & DEF~+2 & RES~+1 \\ 
	\textbf{Level 7:} & HP~+5  & MP~+10 & STR~+2 &        \\ 
	\textbf{Level 8:} & HP~+10 & MP~+5  & RES~+2 &        \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & STR~+2 &        \\ 
	\textbf{Level 10:}& HP~+10 & MP~+5  & DEF~+1 & STR~+1 \\ 
}
{First Strike}
{	
	At the start of each battle you automatically get the highest possible result for your initiative check.
}
{Counter Attack}
{	
	Whenever an enemy successfully hits you with an \hyperlink{action}{Attack}, you can immediately make an \hyperlink{action}{Attack} on him.
}
\vfill
\atypet{Treasure Hunter}
{		
	\textbf{Level 4:} & HP~+5  & MP~+10 & RES~+1 & DEF~+1 \\ 
	\textbf{Level 5:} & HP~+10 & MP~+5  & STR~+1 & DEF~+1 \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & STR~+1 & RES~+1 \\ 
	\textbf{Level 7:} & HP~+10 & MP~+10 & DEF~+1 & 	      \\ 
	\textbf{Level 8:} & HP~+5  & MP~+10 & STR~+1 & DEF~+1 \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & RES~+2 &  	  \\ 
	\textbf{Level 10:}& HP~+10 & MP~+10 & STR~+1 &		  \\ 
}
{Gilionaire}
{	
	Enemies drop twice the amount of Gil as usual, when slain by you.
}
{Counter Steal}
{	
	Whenever you successfully evade an \hyperlink{action}{Attack} by an enemy, you can immediately use "Steal Gil" or "Steal Item" on him without any cost.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\techt{\hypertarget{tab}{Steal Gil}}{3}{0r}{Single}{Weapon}
{
	Make a DC 7 check and "borrow" up to 2d~x~10 Gil from the target if you succeed. 
}{}{1}
\techt{Flee}{5}{1r}{2u}{Self}
{
	You and all allies within the target area can move twice the usual distance when running away from enemies for 3 rounds.
}{}{2}
\techt{Steal Item}{5}{0r}{Single}{Weapon}
{
	Make a DC 7 check and "borrow" an \hyperlink{item}{Item} from the target if you succeed. 
	Roll 1d and the item is a \hyperlink{item}{Potion} on a 1-3, a \hyperlink{item}{Remedy} on a 4, an \hyperlink{item}{Ether} on a 5 and a \hyperlink{item}{Phoenix Down} on a 6. 
	The item may also be determined in any other way by the GM.
}{}{3}
\techt{Vanish}{10}{1r}{Single}{Weapon}
{
	You become invisible for up to 1 minute (6 rounds) or until you take an action.
	While invisible, you gain \hyperlink{status}{Blink} and have \hyperlink{check}{Advantage} on all stealing related checks. Also, if you hit an \hyperlink{action}{Attack} while invisible, you automatically score a \hyperlink{action}{Critical Hit}.
}{\blink}{5}
\techt{Mug}{6}{0r}{Single}{Weapon}{
	Make an \hyperlink{action}{Attack} against the target. 
	If you hit, steal 4d~x~10 Gil from him on top of the damage dealt.
}{}{6}
\techt{Quick Pockets}{7}{0r}{Single}{1u}{
	You use two \hyperlink{action}{Items} on the same turn.
}{}{7}
\techt{Throw}{4}{0r}{Single}{4u}{
	You throw a piece of equipment from your inventory on the target, dealing 8d damage if it is a weapon and 5d damage otherwise.
	Then, you make a DC 8 check and the equipment is destroyed upon failure.
}{}{8}
\techt{Bribe}{5}{1r}{Single}{1u}{
	You pay an amount of Gil to the target and make a check with DC 13 minus 1 per every 100 Gil you paid.
	If you succeed, the target leaves the battlefield.
	Some enemies may be \hyperlink{status}{Immune} to this effect. 
}{}{9}
\techt{Mimic}{?}{0r}{?}{?}{
	You use an ability that was used by an ally or enemy on the battlefield within the previous round. 
	In doing this, you have to respect the MP cost, cast time, target and range specifications of the copied ability.
}{}{10}
\pagebreak
