\thispagestyle{empty}
\subsection*{\huge Time Mage}
\vspace{0.3cm}
"Playtime is over!" \\
\indent -- Ultimecia 
\vspace{0.3cm} \\
Time Mages are masters of time and space, who understand that imagination is more important than knowledge. 
They can the manipulate the flow of time and bend the fabric of reality to their advantage. 
While Time Mages rarely fight on their own, they can greatly influence an ongoing battle with their incredible abilities. \\
\vfill
\battrt{
	\textbf{Level 1:} & HP~+17 & MP~+25 & AGI~+2 & MAG~+1 \\
	\textbf{Level 2:} & HP~+5  & MP~+10 & RES~+1 & STR~+1 \\
	\textbf{Level 3:} & HP~+10 & MP~+10 & DEF~+1 &        \\
}{Staff}{Robe}
\vfill
\atypet{Illusionist}
{	
	\textbf{Level 4:} & HP~+5  & MP~+10 & MAG~+2 &        \\ 
	\textbf{Level 5:} & HP~+10 & MP~+10 & RES~+1 &		  \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & DEF~+1 & RES~+1 \\ 
	\textbf{Level 7:} & HP~+5  & MP~+10 & MAG~+1 & RES~+1 \\ 
	\textbf{Level 8:} & HP~+5  & MP~+10 & DEF~+1 & MAG~+1 \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & RES~+2 &        \\ 
	\textbf{Level 10:}& HP~+5  & MP~+10 & MAG~+2 &		  \\ 
}
{Momentum}
{	
	Whenever you move at least 1u towards the target before casting a spell, its range is increased by 1u.
}
{Warp Evade}
{	
	Whenever you are \hyperlink{action}{Attacked}, you can evade by teleporting to a location of your choice within 3u. 
	Afterwards, you cannot use any ability for 1 round including this one.
	You also cannot use this ability while concentrating.
}
\vfill
\atypet{Oracle}
{		
	\textbf{Level 4:} & HP~+10 & MP~+5  & RES~+1 & MAG~+1 \\ 
	\textbf{Level 5:} & HP~+5  & MP~+10 & MAG~+1 & RES~+1 \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & DEF~+2 &		   \\ 
	\textbf{Level 7:} & HP~+10 & MP~+10 & RES~+1 & 	      \\ 
	\textbf{Level 8:} & HP~+5  & MP~+10 & MAG~+2 &        \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & RES~+1 & MAG~+1 \\ 
	\textbf{Level 10:}& HP~+5  & MP~+10 & RES~+2 &        \\ 
}
{Read Ahead}
{	
	You can always detect the presence of hostile characters or monsters within 50u.
}
{Karma}
{	
	You always have one die in reserve with the very first one being a 6. 
	Whenever someone within 3u of you (including yourself) makes a dice roll, you can alter the result by swapping one of the rolled dice with your reserve die if the roller allows you to do so.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\spellt{Gravity}{5}{1r}{Single}{3u}{
	The target suffers 1d damage and can only move half his usual distance on his next turn. 
}{}{1}
\spellt{Slow}{10}{1r}{Single}{3u}{
	For the next 3 rounds the target may either move or take an action on his turn but not both and all of his cast times are increased by 1 round.
}{}{2}
\spellt{Haste}{10}{1r}{Single}{3u}{
	For the next 3 rounds the target may either make an additional movement or action on his turn and all of his cast times are reduced by 1 round.
}{}{3}
\spellt{Graviga}{16}{2r}{2u}{5u}{
	Everyone in the target area suffers 4d damage and can only move half their usual distance on their next turn. 
}{}{5}
\spellt{Extend}{9}{0r}{Single}{5u}{
	Choose a target that benefits or suffers from an effect that lasts for a limited duration.
	The duration of the effect is extended by 2 rounds.
}{}{6}
\spellt{Warp}{14}{1r}{1u}{10u}{
	You teleport to an unoccupied location of your choice that you can see within 10u.
}{}{6}
\spellt{Quicken}{20}{0r}{Single}{3u}{
	The target gets to take an extra turn immediately after you.
	This effect does not change the turn order.
}{}{7}
\spellt{Float}{12}{1r}{Single}{3u}{
	The target can levitate up to 3u above the ground from where he can move his usual distance for 3 rounds.
	He also cannot suffer any \hyperlink{type}{earth} damage while floating.
}{}{8}
\spellt{Stop}{32}{1r}{100u}{Self}{
	You freeze time for everyone in the target area except yourself for up to 1 minute (6 rounds).
	Once you \hyperlink{action}{Attack} or cast \hyperlink{action}{Magic}, time unfreezes again. 
}{}{9}
\spellt{Paradox}{45}{0r}{100u}{Self}{
	You turn back time inside the target area by 10 seconds (1 round).
	All affected entities return to the state (HP, MP, Status Effects) and position they were in one round ago.
	However, your current MP is not subject the effect of "Paradox".
	Also, all affected targets except you have no recollection of occurrences in the last round.	
}{}{10}
\pagebreak
