\thispagestyle{empty}
\subsection*{\huge White Mage}
\vspace{0.3cm}
"Hey, that’s Cloud’s line! ’...It’s too dangerous, I can’t get you involved...’ Blah blah blah." \\
\indent -- Aerith 
\vspace{0.3cm} \\
White mages are experts of defensive magic and
boast a variety of recovery and protective spells.
While mediocre in physical combat, they also feature incredible resistance against magic. Where
others will succumb to the God of Death, a skilled
White Mage will face him and say: "Not today".
\vfill
\battrt{
	\textbf{Level 1:} & HP~+19 & MP~+22 & AGI~+2 & RES~+1 \\
	\textbf{Level 2:} & HP~+5  & MP~+10 & MAG~+1 & STR~+1 \\
	\textbf{Level 3:} & HP~+10 & MP~+5  & RES~+1 & DEF~+1 \\
}{Staff}{Robe}
\vfill
\atypet{Sage}
{	
	\textbf{Level 4:} & HP~+10 & MP~+10 & MAG~+1 & 		  \\ 
	\textbf{Level 5:} & HP~+5  & MP~+10 & MAG~+1 & RES~+1 \\ 
	\textbf{Level 6:} & HP~+5  & MP~+10 & DEF~+1 & MAG~+1 \\ 
	\textbf{Level 7:} & HP~+10 & MP~+10 & MAG~+1 & 	      \\ 
	\textbf{Level 8:} & HP~+5  & MP~+10 & RES~+2 & 		  \\ 
	\textbf{Level 9:} & HP~+10 & MP~+10 & MAG~+1 & 		  \\ 
	\textbf{Level 10:}& HP~+10 & MP~+10 & MAG~+1 & 	      \\  
}
{Sap}
{	
	Whenever you inflict \hyperlink{type}{magical} damage or \hyperlink{status}{Status Effects} to an enemy, increase your MP by 1d.
}
{Barrier}
{	
	Whenever you would be affected by a spell that you are not the primary target of, you can choose to be completely unaffected.
}
\vfill
\atypet{Seer}
{		
	\textbf{Level 4:} & HP~+5  & MP~+5  & MAG~+2 & DEF~+1 \\ 
	\textbf{Level 5:} & HP~+5  & MP~+10 & RES~+2 &		  \\ 
	\textbf{Level 6:} & HP~+10 & MP~+10 & MAG~+1 &        \\ 
	\textbf{Level 7:} & HP~+5  & MP~+10 & RES~+1 & DEF~+1 \\ 
	\textbf{Level 8:} & HP~+10 & MP~+10 & MAG~+1 &		  \\ 
	\textbf{Level 9:} & HP~+5  & MP~+10 & RES~+2 &	      \\ 
	\textbf{Level 10:}& HP~+10 & MP~+10 & RES~+1 &	      \\ 
}
{Doctor's Code}
{	
	Whenever you heal a target's HP you can also make a DC~8 check.
	If you succeed, you may remove one \hyperlink{status}{Status Effect} that the target is suffering from except \hyperlink{status}{KO}.
}
{Absorb MP}
{	
	Whenever you are the target of an ability, increase your MP by half the amount that the caster spent on the action.
}
\pagebreak \\
\noindent {\Large\color{accent}\bf \uline{Abilities\phantom{y}\hfill}}\\\\
\spellt{Cure}{4}{1r}{Single}{3u}{
	The target regains 2d HP. 
}{}{1}
\spellt{Protect}{5}{1r}{Single}{3u}{
	The target gains \hyperlink{status}{EnDEF} for 3 rounds.
}{\enndef}{2}
\spellt{Shell}{5}{1r}{Single}{3u}{
	The target gains \hyperlink{status}{EnRES} for 3 rounds.
}{\enres}{2}
\spellt{Water}{8}{1r}{Single}{4u}{
	You deal 3d \hyperlink{type}{water} damage to the target. 
}{\water}{3}
\spellt{Aero}{8}{1r}{Single}{4u}{
	You deal 3d \hyperlink{type}{wind} damage to the target. 
}{\wind}{3}
\spellt{Sleep}{6}{1r}{Single}{3u}{
	The target makes a DC 8 check and suffers \hyperlink{status}{Sleep} for 3 rounds upon failure.
}{\sleep}{5}
\spellt{Silence}{6}{1r}{Single}{3u}{
	The target makes a DC 8 check and suffers \hyperlink{status}{Silence} for 3 rounds upon failure.
}{\silence}{5}
\spellt{Curaga}{16}{2r}{1u}{5u}{
	Everyone in the target area regains 6d HP. 
}{}{6}
\spellt{Esunaga}{12}{1r}{2u}{5u}{
	You remove all \hyperlink{status}{Status Effects} except \hyperlink{status}{KO} from everyone in the target area.
}{}{7}
\spellt{Life}{24}{2r}{Single}{3u}{
	Remove \hyperlink{status}{KO} status from the target and increase his HP by 2d.
}{\ko}{8}
\spellt{Holy}{26}{3r}{Single}{5u}{
	You deal 8d+20 \hyperlink{type}{holy} damage to the target. 
}{\holy}{9}
\spellt{Auto-Life}{36}{3r}{Single}{3u}{
	You summon a guardian angel that watches over the target. 
	The next time he falls \hyperlink{status}{KO}, he is instantly revived with 1 HP.
}{\ko}{10}
\pagebreak