\ofchapterwithquote{Tech List}{"Now I know why I have these stupid muscles!"}{Sabin}
%
%
\oftech{Jump}{4}{1}{Ranged}{HP+8, MP+12, STR+2}{When you begin casting, you are removed from your row and you can only be targeted by Ranged \& Artillery effects. When Jump takes effect, one target suffers 2d damage and you return to your original position.}\vfill
\oftech{Lancet}{4}{1}{Ranged}{HP+10, MP+10, STR+1, DEF+1}{Reduce one target's HP and MP by your LV and increase your own HP and MP by the same amount.}\vfill
\oftech{Kick}{6}{1}{Melee}{HP+13, MP+7, STR+2}{Two targets suffer 2d damage.}\vfill
\oftech{Guard}{2}{1}{Self}{HP+15, MP+5, DEF+2}{You gain EnDEF for 3r.}\vfill
\oftech{First Aid}{4}{1}{Close}{HP+12, MP+8, DEF+1, RES+1}{One target regains 1d HP. The total amount healed is doubled if you have received no damage while concentrating on this ability.}\vfill
\oftech{Libra}{4}{1}{Ranged}{HP+11, MP+14, RES+1}{You find out one target's Resiliences, Weaknesses, Immunities, as well as his current HP and MP.}\vfill
\oftech{Lay Trap}{4}{1}{Ranged}{HP+13, MP+12, DEF+1}{The next time an enemy uses the Switch Row action, it is negated and he suffers 2d damage. This effect does not stack and it is removed when activated or after 3r.}\vfill
\oftech{Flee}{4}{1}{Close}{HP+7, MP+18, DEF+1, RES+1}{Make a DC6 check, if you pass, everyone in your row may flee the battle.}\vfill
\oftech{Cheer}{4}{1}{Close}{HP+8, MP+12, STR+2}{One target gains EnSTR for 3r.}\vfill
\oftech{Steal}{4}{1}{Melee}{HP+10, MP+15, STR+1}{Make a DC7 check and roll 1d if you pass. You get LV times 20G on 1 or 2, a Potion on a 3, a Remedy on a 4, an Ether on a 5 and a Phoenix Down on a 6. Alternatively, the GM may choose the reward.}\newpage
%
\oftech{Elemental Strike}{5}{4}{Melee}{HP+11, MP+9, STR+1, MAG+1}{The target suffers 2d damage with an elemental type of your choice. Also, add your MAG to the damage.}\vfill
\oftech{Piercethrough}{6}{4}{Ranged}{HP+13, MP+7, STR+2}{One target in the Front Row and one in the Back Row suffer 2d damage.}\vfill
\oftech{Fire Breath}{7}{4}{Melee}{HP+9, MP+11, STR+1, DEF+1}{All targets in a row suffer 2d fire damage.}\vfill
\oftech{Beatdown}{5}{4}{Melee}{HP+15, MP+5, STR+2}{Make an Attack check with Disadvantage against one target. If you pass, he suffers 5d damage.}\vfill
\oftech{Defensebreak}{6}{4}{Melee}{HP+12, MP+8, DEF+2}{One target suffers 2d damage and DeDEF for 2r.}\vfill
\oftech{Powerbreak}{6}{4}{Melee}{HP+14, MP+6, STR+1, DEF+1}{One target suffers 2d damage and DeSTR for 2r.}\vfill
\oftech{Improvise}{6}{4}{Close}{HP+8, MP+17, STR+1}{Roll 1d, based on the result, one target gains a Status Effect for 3r: 1-EnDEF, 2-EnRES, 3-EnSTR, 4-Blink, 5-Regen, 6-Haste.}\vfill
\oftech{Lullaby}{9}{4}{Melee}{HP+7, MP+13, RES+2\hfill Requires: Cheer}{All targets in a row make a DC7 check and suffer Sleep for 1r upon failure.}\vfill
%
\oftech{Blade Dance}{10}{6}{Melee}{HP+13, MP+7, STR+2}{All targets in a row suffer 2d damage.}\vfill
\oftech{Dragon Dive}{12}{6}{Ranged}{HP+8, MP+12, STR+2\hfill Requires: Jump}{Has the same effect as Jump, except it causes 2d fire damage to all targets in a row.}\vfill
\oftech{Aurablast}{8}{6}{Ranged}{HP+11, MP+14, STR+1\hfill Requires: Kick}{One target suffers magical damage equal to your LV.}\vfill
\oftech{Rush}{8}{6}{Melee}{HP+14, MP+6, STR+1, DEF+1}{One target makes a DC8 check and upon failure suffers 2d damage and is pushed into the Back Row.}\clearpage
\oftech{Mediguard}{12}{6}{Ranged}{HP+15, MP+5, DEF+2\hfill Requires Guard}{You gain EnDEF, EnRES and Regen for 3r.}\vfill
\oftech{Revive}{12}{6}{Close}{HP+9, MP+11, DEF+1, RES+1\hfill Requires: First Aid}{Remove KO from one target and increase his HP by 1.}\vfill
\oftech{Healing Wind}{10}{6}{Ranged}{HP+8, MP+12, RES+2\hfill Requires: First Aid}{One target in the Front Row \& one in the Back Row regain 3d HP.}\vfill
\oftech{Smoke Bomb}{10}{6}{Melee}{HP+10, MP+15, DEF+1\hfill Requires: Lay Trap}{All targets in a row make a DC8 check and suffer Blind for 3r upon failure.}\vfill
\oftech{Vanish}{8}{6}{Close}{HP+9, MP+16, STR+1\hfill Requires: Flee}{You gain Blink for up to 3r rounds. Your next Attack is a Critical Hit and ends this effect.}\vfill
%
\oftech{Requiem}{4}{8}{Ranged}{HP+7, MP+13, STR+1, RES+1\hfill Requires: Lullaby}{One target makes a DC8 check and upon failure he suffers 3d dark and Zombie for 3r.}\vfill
\oftech{Razor Gale}{4}{8}{Ranged}{HP+13, MP+12, STR+1\hfill Requires: Aurablast}{One target in the Front Row and one in the Back Row suffer 3d wind damage.}\vfill
\oftech{Threaten}{4}{8}{Ranged}{HP+12, MP+8, STR+1, DEF+1}{The target makes a DC8 check and upon failure suffers 3d damage and Silence for 3r.}\vfill
\oftech{Provoke}{9}{8}{Ranged}{HP+14, MP+6, DEF+2}{The target makes a DC7 check and upon failure he has to target you with an action on his next turn.}\vfill
\oftech{Aim}{8}{8}{Ranged}{HP+7, MP+13, STR+2\hfill Requires: Libra}{For the next 3r you have Advantage on all Attack checks.}\vfill
\oftech{Throw}{8}{8}{Ranged}{HP+9, MP+11, STR+2\hfill Requires: Vanish}{Throw a weapon from your inventory onto one target to deal 4d damage. You can collect all thrown objects at the end of the battle.}\vfill
\oftech{Mix}{14}{8}{Melee}{HP+9, MP+16, DEF+1\hfill Requires: Steal}{Use 2 Items on the target and roll 1d. Targeted allies additionally recover 3d HP on 1-2, gain Blink for 3r on 3-4 and Haste for 3r on 5-6. Targeted enemies additionally suffer 3d damage on 1-2, Poison for 3r on 3-4 and Blind for 3r on 5-6.}\vfill
\oftech{Blitz}{4}{8}{Ranged}{HP+13, MP+7, STR+2\hfill Requires: Kick}{Use two different Techs consecutively in the same turn. You have to respect additional MP costs of both Techs and you take 4d damage.}\vfill
\oftech{Army of One}{4}{12}{Artillery}{HP+12, MP+8, STR+1, DEF+1\hfill Requires: Blade Dance}{All enemies suffer 3d damage.}\vfill
%
\oftech{Highwind}{23}{10}{Artillery}{HP+9, MP+11, STR+2, RES+1\hfill Requires: Dragon Dive}{Has the same effect as Jump, except it causes 4d wind damage to all enemies.}\vfill
\oftech{Final Heaven}{24}{10}{Melee}{HP+8, MP+7, STR+3\hfill Requires: Blitz}{The target suffers 4d damage and makes a DC9 check. Upon failure he suffers another 2d damage and is pushed into the back row.}\vfill
\oftech{Omnislash}{24}{10}{Melee}{HP+9, MP+6, STR+2, DEF+1\hfill Requires: Army of One}{Make 3 DC7 checks. One target suffers 3d damage for each pass and 1d for each fail. Also the STR added to the damage is tripled.}\vfill
\oftech{Barrage}{21}{10}{Self}{HP+5, MP+5, STR+3\hfill Requires: Aim}{For 3r, you gain Haste and EnSTR and all your Attacks target an entire row.}\vfill
\oftech{Mighty Guard}{22}{10}{Ranged}{HP+12, MP+3, DEF+2, RES+1\hfill Requires: Mediguard}{For 3r you gain Resilience against physical damage.}\vfill
\oftech{Mimic}{?}{10}{?}{HP+3, MP+22, STR+1\hfill Requires: Improvise}{You use an ability that was used by an ally or enemy on the battlefield since your last turn.}\vfill
\oftech{Pandora's Box}{25}{4}{Artillery}{HP+5, MP+20, DEF+1\hfill Requires: Mix}{All enemies suffer 1d damage, roll 1d and suffer a Status Effect for 3r based on the result: 1-DeDEF, 2-Zombie, 3-Silence, 4-Poison, 5-Blind, 6-Sleep.}
%
\clearpage
%
\ofchapterwithquote{Spell List}{"Oh, I’ll show you how lightning strikes."}{Lightning}
%
\ofspell{Fire}{4}{1}{Ranged}{HP+8, MP+12, MAG+2}{One target suffers 2d fire damage.}\vfill
\ofspell{Thunder}{4}{1}{Ranged}{HP+7, MP+13, MAG+2}{One target suffers 2d lightning damage.}\vfill
\ofspell{Blizzard}{4}{1}{Ranged}{HP+6, MP+14, MAG+2}{One target suffers 2d ice damage.}\vfill
\ofspell{Cure}{4}{1}{Ranged}{HP+5, MP+15, MAG+1, DEF+1}{One target regains 2d HP.}\vfill
\ofspell{Protect}{4}{1}{Melee}{HP+8, MP+12, DEF+2}{One target gains EnDEF for 3r.}\vfill
\ofspell{Shell}{4}{1}{Melee}{HP+8, MP+12, RES+2}{One target gains EnRES for 3r.}\vfill
\ofspell{Esuna}{5}{1}{Ranged}{HP+6, MP+14, RES+1, DEF+1}{Remove all negative Status Effects from one target except KO.}\vfill
\ofspell{Poison}{4}{1}{Ranged}{HP+10, MP+15, RES+1}{One target makes a DC8 check and suffers Poison for 3r upon failure.}\vfill
\ofspell{Blind}{4}{1}{Ranged}{HP+9, MP+16, RES+1}{One target makes a DC8 check and suffers Blind for 3r upon failure.}\vfill
\ofspell{Sleep}{4}{1}{Ranged}{HP+8, MP+17, RES+1}{One target makes a DC8 check and suffers Sleep for 3r upon failure.}\vfill
\ofspell{Silence}{4}{1}{Ranged}{HP+7, MP+18, RES+1}{One target makes a DC8 check and suffers Silence for 3r upon failure.}\newpage
\ofspell{Gravity}{6}{1}{Ranged}{HP+4, MP+16, MAG+1, RES+1}{One target suffers 2d dark damage and his EVA is reduced by 1 for 1r.}\vfill
%
\ofspell{Extend}{4}{4}{Artillery}{HP+10, MP+10, DEF+1, RES+1}{The duration of all Status Effects active on one target are extended by 3r.}\vfill
\ofspell{Warp}{8}{4}{Close}{HP+7, MP+18, RES+1}{Make a DC6 check, if you pass, both you and another close target successfully flee the battle.}\vfill
\ofspell{Zombify}{8}{4}{Ranged}{HP+6, MP+14, MAG+1, RES+1}{One target makes a DC8 check and suffers 2d dark damage and Zombie for 3r upon failure.}\vfill
\ofspell{Aero}{7}{4}{Ranged}{HP+9, MP+11, MAG+2}{One target suffers 3d wind damage.}\vfill
\ofspell{Bio}{8}{4}{Ranged}{HP+7, MP+18, MAG+1\hfill Requires: Poison}{One target makes a DC8 check and suffers 2d damage and Poison for 3r upon failure. \\ \acc{Requires:} Poison}\vfill
\ofspell{Haste}{8}{4}{Melee}{HP+5, MP+20, RES+1}{One target gains Haste for 3r.}\vfill
\ofspell{Regen}{6}{4}{Melee}{HP+8, MP+12, MAG+1, RES+1}{One target gains Regen for 3r.}\vfill
\ofspell{Image}{6}{4}{Melee}{HP+6, MP+19, DEF+1}{One target gains Blink for 3r.}\vfill
\ofspell{Raise}{14}{4}{Melee}{HP+9, MP+11, RES+2}{Remove KO from one target and increase his HP by 1.}\vfill
%
\ofspell{Osmosis}{0}{6}{Ranged}{HP+4, MP+21, MAG+1}{Reduce one target's MP by your MAG and increase your MP by the same amount.}\vfill
\ofspell{Curaga}{12}{6}{Ranged}{HP+5, MP+15, MAG+1, DEF+1\hfill Requires: Cure}{All targets in a row regain 4d HP.}\newpage
\ofspell{Firaga}{12}{6}{Ranged}{HP+8, MP+12, MAG+2\hfill Requires: Fire}{All targets in a row suffer 4d fire damage.}\vfill
\ofspell{Thundaga}{12}{6}{Ranged}{HP+7, MP+13, MAG+2\hfill Requires: Thunder}{All targets in a row suffer 4d lightning damage.}\vfill
\ofspell{Blizzaga}{12}{6}{Ranged}{HP+6, MP+14, MAG+2\hfill Requires: Blizzard}{All targets in a row suffer 4d ice damage.}\vfill
\ofspell{Graviga}{16}{6}{Ranged}{HP+4, MP+16, MAG+1, RES+1\hfill Requires: Gravity}{All targets in a row suffer 4d dark damage and their EVA is reduced by 1 for 1r.}\vfill
\ofspell{NulElement}{16}{6}{Ranged}{HP+8, MP+12, RES+2\hfill Requires: Shell}{Choose an element (e.g. fire). One target does not suffer any damage of the chosen element for 3r.}\vfill
\ofspell{Quicken}{18}{6}{Ranged}{HP+5, MP+20, RES+1\hfill Requires: Haste}{One target takes an extra turn immediately after yours, then the round continues as usual. You can only use this ability once per round.}\vfill
\ofspell{Imperil}{10}{6}{Ranged}{HP+10, MP+10, DEF+1, RES+1}{One target suffers DeDEF and DeRES for 3r.}\vfill
\ofspell{Wall}{10}{6}{Ranged}{HP+10, MP+10, DEF+1, RES+1\hfill Requires: Protect}{One target gains EnDEF and EnRES for 3r.}\vfill
%Comet
%
\ofspell{Quake}{22}{8}{Artillery}{HP+10, MP+10, MAG+2}{All targets in a row suffer 6d earth damage.}\vfill
\ofspell{Doom}{20}{8}{Ranged}{HP+6, MP+14, MAG+1, RES+1\hfill Requires: Zombify}{One target suffers KO after 3r. If he is immune to KO, he suffers 6d dark damage after 3r instead.}\vfill
\ofspell{Aeroga}{20}{8}{Ranged}{HP+9, MP+11, MAG+2\hfill Requires: Aero}{All targets in a row suffer 3d wind damage and make a DC6 check. Upon failure, they are pushed into the other row.}\vfill
\ofspell{Drain}{16}{8}{Ranged}{HP+16, MP+9, MAG+1\hfill Requires: Osmosis}{One target suffers 2d dark damage and you regain HP equal to the total damage dealt.}\newpage
\ofspell{Dispel}{12}{8}{Artillery}{HP+6, MP+14, RES+1, DEF+1\hfill Requires: Esuna}{All Resiliences and active beneficial Status Effects of one target are removed for 3r.}\vfill
\ofspell{Full-Life}{24}{8}{Ranged}{HP+9, MP+11, RES+2\hfill Requires: Raise}{Remove KO from one target and fully restore his HP.}\vfill
\ofspell{Reflect}{16}{8}{Melee}{HP+9, MP+16, RES+1\hfill Requies: Wall}{One target gains a shield that reflects the next spell that targets them back to its caster. This effect does not stack.}\vfill
\ofspell{Stop}{18}{8}{Ranged}{HP+7, MP+18, RES+1\hfill Requires: Extend}{All targets in a row make a DC9 check and suffer Sleep for 1 round upon failure.}\vfill
\ofspell{Exchange}{12}{8}{Melee}{HP+12, MP+13, DEF+1\hfill Requires: Warp}{Switch your position with an ally in the other row.}\vfill
%
\ofspell{Auto-Life}{32}{10}{Artillery}{HP+8, MP+17, RES+1\hfill Requires: Full-Life}{The next time one target falls KO, he is instantly revived with 1 HP. If unused, this effect expires after 10r.}\vfill
\ofspell{Holy}{32}{10}{Artillery}{HP+5, MP+15, MAG+2\hfill Reqiures: Curaga}{One target suffers 6d+10 holy damage.}\vfill
\ofspell{Flare}{32}{10}{Artillery}{HP+4, MP+6, MAG+3\hfill Requires: Firaga}{One target suffers 6d+10 fire damage.}\vfill
\ofspell{Ultima}{35}{10}{Artillery}{HP+3, MP+7, MAG+3\hfill Requires: 3 LV8 spells}{All enemies suffer 6d dark damage.}\vfill
\ofspell{Banish}{28}{10}{Artillery}{HP+7, MP+18, MAG+1\hfill Requires: Stop}{One target is removed from the battlefield and cannot take actions for 3r. You cannot target the same combatant with this effect more than once per battle.}\vfill
\ofspell{Dualcast}{0}{10}{Self}{HP+5, MP+20, MAG+1\hfill Requires: 4 LV1 spells}{Cast two spells that are LV4 or lower simultaneously, but need to spend the necessary MP for both.}\vfill
\ofspell{Meteor}{35}{10}{Artillery}{HP+6, MP+4, MAG+3\hfill Requires: Graviga}{After 3r, all enemies suffer 6d+30 damage. You cannot cast this ability again in the meantime.}
%
\clearpage
%
\ofchapterwithquote{Passive List}{"Welcome to your doom, starring me!"}{Rikku}
%
\ofpassive{Analyze}{HP+9, MP+16, MAG+1}{When you deal magical damage, you can learn one of the following aspects about the target: Resiliences, Weaknesses, Immunities, current HP, current MP.}\vfill
\ofpassive{Dress To Impress}{HP+13, MP+7, DEF+1, RES+1}{You can equip an extra Accessory. For each equipped Accessory you gain DEF +1 \& RES +1.}\vfill
\ofpassive{Encore}{HP+8, MP+12, RES+2}{When you bestow one or more positive Status Effects on a target, they also regain HP equal to your LV.}\vfill
\ofpassive{Unscarred}{HP+12, MP+8, STR+2}{While your HP is at its maximum, double the STR \& MAG bonus added to your Attacks, Techs \& Magic.}\vfill
\ofpassive{Lifestream}{HP+14, MP+11, STR+1}{When you do not have enough MP to use Techs \& Magic you can pay the same amount of HP instead.}\vfill
\ofpassive{Overwhelm}{HP+10, MP+10, RES+1}{After you inflict elemental damage, the target gets a Weakness to that type until the end of your next turn.}\vfill
\ofpassive{Camouflage}{HP+9, MP+11, DEF+1, RES+1}{When you Switch Row, you gain Blink for 1r.}\vfill
\ofpassive{Twilight Warrior}{HP+10, MP+10, MAG+1, STR+1}{You may add the holy or dark type to the damage dealt by your Magic \& Techs.}\vfill
\ofpassive{Holy Guard}{HP+13, MP+7, DEF+1, RES+1}{As long as there is at least one ally in the same row, you and all allies in the same row gain EnRES.}\vfill
\ofpassive{Gilionaire}{HP+8, MP+12, STR+1}{When you deal damage to an enemy, you also receive an amount of Gil equal to the total damage dealt.}\newpage
\ofpassive{Item Lore}{HP+9, MP+16, DEF+1}{You can use all Melee Items as Artillery and when using single target Items, you can affect an additional target in the same row.}\vfill
\ofpassive{Tunneling}{HP+5, MP+20, MAG+1}{When you use a Ranged ability, you can increase it's range to Artillery by doubling its MP cost.}\vfill
\ofpassive{Souleater}{HP+14, MP+11, STR+1}{When you deal damage an enemy you also may deal dark damage equal to your LV to all enemies in the same row and yourself.}\vfill
\ofpassive{Doctor's Code}{HP+7, MP+13, DEF+1, RES+1}{When you use an ability on a Close target, you can additionally use an Item on him.}\vfill
\ofpassive{Rally}{HP+12, MP+8, DEF+1, RES+1}{At the start of every turn, you regain 2~HP for every ally in the same row.}\vfill
\ofpassive{War Cry}{HP+7, MP+13, STR+1, MAG+1}{While your HP is lower than half its maximum, your damage ignores the target's DEF \& RES.}\vfill
\ofpassive{Blessing}{HP+8, MP+12, STR+1, MAG+1}{When you restore your or an ally's HP, the target additionally gains EnSTR and EnMAG for 1r.}\vfill
\ofpassive{Field Cast}{HP+6, MP+14, MAG+2}{When you deal magical damage to a single target, you can instead deal half the amount to the entire row.}\vfill
\ofpassive{Duelist}{HP+13, MP+7, STR+1, DEF+1}{As long as only you and one enemy are in the Front Row, you gain Blink, EnSTR and EnDEF.}\vfill
\ofpassive{Concentrate}{HP+11, MP+9, STR+2}{Add 1 to the result of all your Attack checks.}\vfill
\ofpassive{Recoil}{HP+6, MP+14, STR+1, DEF+1}{When you Attack, you may also move to the Back Row.}
%
\clearpage
%
\ofchapterwithquote{Reaction List}{"I dreamt I was a moron."}{Squall}
%
\ofreaction{Dirty Dancing}{HP+8, MP+12, DEF+2}{When you evade an Attack, the Attacker suffers Zombie, Poison or Blind for 1r.}\vfill
\ofreaction{Gaia's Shield}{HP+11, MP+9, DEF+1, RES+1}{When you suffer elemental damage, double your DEF and RES for calculating the damage received.}\vfill
\ofreaction{Learn}{HP+7, MP+13, STR+1, MAG+1}{When you are targeted by an ability, you can make a DC8 check and if you succeed, you learn how to use it. You can only know one ability like this, but you can choose to forget your current one.}\vfill
\ofreaction{Block}{HP+13, MP+7, DEF+2}{When an enemy tries to Switch Row, he has to first succeed a DC7 check.}\vfill
\ofreaction{Magic Evade}{HP+6, MP+14, RES+2}{You can evade Magic by passing a DC9 check.}\vfill
\ofreaction{Strikeback}{HP+12, MP+8, STR+1, DEF+1}{When you evade an Attack by an enemy, you may immediately Attack him.}\vfill
\ofreaction{Replenish MP}{HP+7, MP+13, DEF+1, RES+1}{When you suffer physical damage, you regain MP equal to half your LV.}\vfill
\ofreaction{Swiftcast}{HP+6, MP+14, MAG+2}{Once per round, when an enemy within range uses an action, you can immediately cast a LV1 spell on him.}\vfill
\ofreaction{Cover}{HP+14, MP+6, DEF+2}{When a Close target takes physical damage, you can direct half the amount to yourself.}\vfill
\ofreaction{Auto-Potion}{HP+11, MP+9, DEF+1, RES+1}{Once per round, when you suffer damage, you can immediately use an Item.}\newpage
\ofreaction{Ballistic Defense}{HP+13, MP+12, DEF+1}{When an enemy rolls lower than 8 on a Ranged Attack Check against you, the damage dealt is halved.}\vfill
\ofreaction{Bushido}{HP+8, MP+12, DEF+2}{You can evade Techs by passing a DC9 check.}\vfill
\ofreaction{Absorb MP}{HP+7, MP+13, RES+2}{When you are targeted by an ability, increase your MP by half the amount spent on it.}\vfill
\ofreaction{Collateral}{HP+8, MP+12, DEF+1, RES+1}{When your entire row or party is targeted, the damage you suffer is halved.}\vfill
\ofreaction{Intimidate}{HP+12, MP+8, STR+1, DEF+1}{When you suffer damage by a Melee enemy, he has to make a DC7 check. Upon failure, all physical damage that he deals on his next turn, is halved.}\vfill
\ofreaction{Shield Bash}{HP+13, MP+7, STR+2}{When you evade an Attack, you can push the attacker into the Back Row.}\vfill
\ofreaction{Scurvy Dog}{HP+8, MP+12, RES+2}{When you are affected by a negative Status Effect that lasts for longer than 1r, its duration is reduced by 1r.}\vfill
\ofreaction{Auto-Regen}{HP+11, MP+9, DEF+1, RES+1}{When you suffer damage, you gain Regen until the end of your next turn.}\vfill
\ofreaction{Mana Shield}{HP+5, MP+15, DEF+1, RES+1}{When your HP is reduced, you can instead reduce your MP by that amount if you have enough.}\vfill
\ofreaction{Stagger}{HP+11, MP+9, STR+1, DEF+1}{Once per round when an ally in the same row Attacks, you may also make an Attack on the same target.}\vfill
\ofreaction{En Garde}{HP+8, MP+12, MAG+1, DEF+1}{You can still evade Attacks while concentrating.}
%
\clearpage