\twocolumn[
\ofsection{Equipment Lists}
%
{\LARGE \accf{Equipment Lists}}
%
\vspace*{0.25cm}\\
%
\parbox{2\columnwidth}{\ofquotewide{"Don’t you know? These days all it takes for your dreams to come true is money and power."}{President Shinra}}
%
\vspace*{0.75cm}\\
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.075\columnwidth} p{0.125\columnwidth} p{1.35\columnwidth}} 
{\oficonweapon\accf{Blades} & \accf{LV} & \accf{STR} & \accf{Value} & \accf{Effect}}
{
	Mythril Blade 	 & 1 & +0 & 250G  & This weapon has an additional Materia slot. \\
	Blood Sword    	 & 1 & +0 & 500G  & When you reduce an enemy to 0 HP, you regain HP equal to your LV. \\
	Buster Sword 	 & 1 & +0 & 500G  & On Critical Hit, triple your usual damage, instead of just doubling it. \\
	Gladius  		 & 1 & +0 & 500G  & When your HP falls below half of its maximum, you gain EnSTR for 3r.\\
	Crystal Blade 	 & 4 & +3 & 1500G & This weapon has an additional Materia slot. \\
	Organyx 	  	 & 4 & +3 & 2000G & Whenever you successfully Attack an enemy, you regain 2 MP. \\
	Gunblade 	  	 & 4 & +3 & 2000G & When you use a Ranged Tech, you can deal an extra 3 damage to its targets.\\
	Assassin's Knife & 4 & +3 & 2000G & On a Critical Hit, the target suffers KO. \\
	Adamant Blade  	 & 8 & +6 & 3000G & This weapon has an additional Materia slot. \\
	Murasame 		 & 8 & +6 & 4000G & While in the Front Row, all your Techs become Ranged. \\
	Save the Queen   & 8 & +6 & 4000G & When your row is targeted by a spell, you can negate it by passing a DC9 check.\\
	Main Gauche  	 & 8 & +6 & 4000G & When you roll 9 or higher on an Attack check, the target suffers Poison for 3r.\\
	Excalibur	 	 & 10& +9 & ???   & Unique. Your Attacks ignore the target's DEF. \\
	%&&&
}
%
\vspace*{0.75cm}\\
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.075\columnwidth} p{0.05\columnwidth} p{0.125\columnwidth} p{1.25\columnwidth}}
{\oficonweapon\accf{Scepters} & \accf{LV} & \accf{MAG} & \accf{MP} & \accf{Value} & \accf{Effect}}
{
	Mythril Scepter 	 & 1 & +1 & +5  & 250G  & This weapon has an additional Materia slot. \\
	Healing Staff 	 	 & 1 & +0 & +10 & 500G  & Whenever you restore HP with Magic, add 2 to the amount. \\ 
	Power Staff 	 	 & 1 & +0 & +10 & 500G  & Add your MAG to the damage dealt by your Attacks. \\
	Lilith Rod 			 & 1 & +2 & +0  & 500G  & When your HP falls below half of its maximum, you gain EnMAG for 3r. \\
	Crystal Scepter 	 & 4 & +2 & +10 & 1500G & This weapon has an additional Materia slot. \\
	Elemental Rod		 & 4 & +4 & +0  & 2000G & When you deal fire, ice or lightning damage, add 2 to the amount.\\
	Malboro Rod			 & 4 & +4 & +0  & 2000G & When you cause one or more negative Status Effects, you regain 3 HP.\\
	Sage's Staff 		 & 4 & +0 & +20 & 2000G & You can add the holy or dark type to damage dealt by Attacks and Magic.\\
	Adamant Scepter 	 & 8 & +3 & +15 & 3000G & This weapon has an additional Materia slot. \\
	Magus Rod 		  	 & 8 & +6 & +0  & 4000G & When you benefit from the EnMAG status, its effect is doubled. \\ 
	Rune Staff 		  	 & 8 & +0 & +30 & 4000G & When you deal magical damage to an enemy suffering a Status Effect, he also suffers Silence for 3r. \\
	Stardust Rod 		 & 8 & +6 & +30 & 4000G & When you reduce an enemy to 0 HP, you regain MP equal to your LV. \\
	Nirvana		 		 & 10& +9 & +40 & ???   & Unique. Your spells ignore their targets' RES.
}
%
\vspace*{0.75cm}\\
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.075\columnwidth} p{0.125\columnwidth} p{1.35\columnwidth}} 
{\oficonweapon\accf{Polearms} & \accf{LV} & \accf{STR} & \accf{Value} & \accf{Effect}}
{
	Mythril Spear 	 & 1 & +0 & 250G  & This weapon has an additional Materia slot. \\
	Longinus 		 & 1 & +0 & 500G  & When you roll 9 or higher on an Attack check, the target suffers Blind for 3r. \\ 
	Naginata		 & 1 & +0 & 500G  & When you switch from back to front row, you may immediately make an Attack.\\
	Crystal Spear 	 & 4 & +3 & 1500G & This weapon has an additional Materia slot. \\
	Trident 		 & 4 & +3 & 2000G & Resilience: water, wind \\
	Vel 		 	 & 4 & +3 & 2000G & The damage dealt by all of your Techs is of magical type. \\
	Adamant Spear 	 & 8 & +6 & 3000G & This weapon has an additional Materia slot. \\
	Gae Bolg 		 & 8 & +6 & 4000G & You may choose 3 targets for Attacks, but then the damage dealt to each is halved. \\
	Zeus Mace 		 & 8 & +6 & 4000G & When you roll 11 or higher on an Attack check, you score a Critical Hit. \\
	Gungnir 		 & 10& +9 & ???   & Unique. Attacks with this weapon are Ranged.
}
%
\vspace*{0.75cm}\\
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.075\columnwidth} p{0.125\columnwidth} p{1.35\columnwidth}} 
{\oficonweapon\accf{Ballistics} & \accf{LV} & \accf{STR} & \accf{Value} & \accf{Effect}}
{
	Mythril Bow 	 & 1 & +0 & 250G  & This weapon has an additional Materia slot. \\
	Tiny Bee 		 & 1 & +0 & 500G  & On Critical Hit, you may immediately take another action.\\
	Elfin Bow 		 & 1 & +0 & 500G  & Add 3 to the damage when you Attack a target that is suffering a Status Effect.\\
	%Spirit Cannon    & 1 & +0 & 500G  & Whenever you successfully Attack a target who is suffering the Zombie status, you score a Critical Hit.\\
	Crystal Bow 	 & 4 & +1 & 1500G & This weapon has an additional Materia slot. \\
	Machine Gun 	 & 4 & +1 & 2000G & If the target evades your Attack, he still suffers half the total damage. \\
	Dragon Breath 	 & 4 & +1 & 2000G & Attacks deal an extra 1d fire damage to everyone in the same row as the target.\\
	%Crossbow		 & 4 & +3 & 2000G & Does not suffer from the penalty of its Type Effect, but its range is only 3u. \\
	Adamant Bow		 & 8 & +2 & 3000G & This weapon has an additional Materia slot. \\
	Fomalhaut 		 & 8 & +2 & 4000G & The damage dealt by this weapon is of magical type. \\
	Killer Bow 		 & 8 & +2 & 4000G & On Critical Hit, the target suffers KO. \\
	Death Penalty	 & 10& +3 & ??? & Unique. Your Attacks cannot be evaded.
}
%
]\twocolumn[
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.075\columnwidth} p{0.075\columnwidth} p{0.125\columnwidth} p{1.225\columnwidth}} 
{\oficonarmor\accf{Light Armor} & \accf{LV} & \accf{DEF} & \accf{RES} & \accf{Value} & \accf{Effect}}
{
	Mythril Vest 	 & 1 & +1 & +1 & 250G  & This armor has an additional Materia slot. \\
	Ninja Gear 	 	 & 1 & +1 & +1 & 500G  & Immunity: DeSTR, DeMAG \\
	Red Jacket 	 	 & 1 & +1 & +1 & 500G  & Resilience: fire \\
	Crystal Vest 	 & 4 & +2 & +2 & 1500G & This armor has an additional Materia slot. \\
	Kenpo Gi 	 	 & 4 & +2 & +2 & 2000G & Immunity: Blind, Silence \\
	Survival Vest 	 & 4 & +2 & +2 & 2000G & Resilience: earth, wind \\
	Adamant Vest 	 & 8 & +3 & +3 & 3000G & This armor has an additional Materia slot. \\
	Power Vest 	 	 & 8 & +3 & +3 & 4000G & STR+2 \\
	Minerva 	 	 & 8 & +3 & +3 & 4000G & Maximum MP +5, Resilience: ice \\
	Brave Suit 	 	 & 10& +4 & +4 & ???   & Unique. EVA~+1
	%Behemoth Suit & RES +1 \\
	%Mirage Vest & Immunity: Sleep \\
	%Gaia Gear & Resilience: earth \\
}
%
\vspace*{0.6cm}\\
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.075\columnwidth} p{0.075\columnwidth} p{0.125\columnwidth} p{1.225\columnwidth}} 
{\oficonarmor\accf{Heavy Armor} & \accf{LV} & \accf{DEF} & \accf{RES} & \accf{Value} & \accf{Effect}}
{
	Mythril Armor 	 & 1 & +2 & +0 & 250G  & This armor has an additional Materia slot. \\
	Fullplate 	 	 & 1 & +1 & +1 & 500G  & Resilience: lightning \\
	Knight's Armor 	 & 1 & +1 & +1 & 500G  & Immunity: DeDEF, DeRES \\
	Crystal Armor 	 & 4 & +3 & +1 & 1500G & This armor has an additional Materia slot. \\
	Dragon Mail 	 & 4 & +3 & +1 & 2000G & Resilience: fire, wind \\
	Mirror Mail 	 & 4 & +3 & +1 & 2000G & Immunity: Silence, Sleep \\
	Adamant Armor 	 & 8 & +4 & +2 & 3000G & This armor has an additional Materia slot. \\
	Demon Mail 	 	 & 8 & +4 & +2 & 4000G & Immunity: Zombie; Resilience: dark, fire \\
	Achilles 	 	 & 8 & +4 & +2 & 4000G & Maximum MP +10 \\
	Genji Armor	 	 & 10& +5 & +3 & ???   & Unique. Maximum HP +15
}
%
\vspace*{0.6cm}\\
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.075\columnwidth} p{0.075\columnwidth} p{0.125\columnwidth} p{1.225\columnwidth}} 
{\oficonarmor\accf{Robes} & \accf{LV} & \accf{DEF} & \accf{RES} & \accf{Value} & \accf{Effect}}
{
	Mythril Robe 	 & 1 & +0 & +2 & 250G  & This armor has an additional Materia slot. \\
	Silk Robe 	 	 & 1 & +0 & +2 & 500G  & Resilience: ice \\
	Black Robe 	 	 & 1 & +0 & +2 & 500G  & Immunity: Poison \\
	Crystal Robe 	 & 4 & +1 & +3 & 1500G & This armor has an additional Materia slot. \\
	Scholar's Robe 	 & 4 & +1 & +3 & 2000G & Maximum MP +5  \\
	Luminous Robe 	 & 4 & +1 & +3 & 2000G & Resilience: holy, fire \\
	Adamant Robe 	 & 8 & +2 & +4 & 3000G & This armor has an additional Materia slot. \\
	Magus Robe 	 	 & 8 & +2 & +4 & 4000G & Immunity: DeATR \\
	White Robe  	 & 8 & +2 & +4 & 4000G & Resilience: dark, lightning \\
	Lorldy Robe 	 & 10& +3 & +5 & ???   & Unique. Maximum MP +15
}
%
\vspace*{0.6cm}\\
%
\oftablewide{p{0.3\columnwidth} p{0.125\columnwidth} p{1.575\columnwidth}}
{\oficonitem\accf{Item} & \accf{Value} & \accf{Effect}}
{
	%Gysahl Greens & 25G & Vegetable well-known as a Chocobo's favorite food. \\
	Antidote & 50G & Removes Poison from a Close target. \\
	Eyedrops & 50G & Removes Blind from a Close target. \\ 
	Echo Grass & 50G & Removes Silence from a Close target. \\ 
	Gold Needle & 50G & Remove Immobile from a Close target. \\
	Arctic Wind & 100G & One Melee target suffers 2d ice damage. \\
	Bomb Fragment & 100G & One Melee target suffers 2d fire damage. \\
	Lightning Gem & 100G & One Melee target suffers 2d lightning damage. \\
	Potion & 100G & One Close target regains 8 HP. \\
	Holy Water & 150G & Removes Zombie from a Close target.\\
	Ether & 150G & One Close target regains 12 MP. \\
	%Light Curtain & 200G & The target gains EnDEF for 3 rounds.\\
	%Lunar Curtain & 200G & The target gains EnRES for 3 rounds. \\
	%Giant's Tonic & 200G & The target gains EnSTR for 3 rounds.\\
	%Faerie's Tonic & 200G & The target gains EnMAG for 3 rounds.\\
	%Elemental Oil & 250G &  This Item is of one elemental type (e.g Fire Oil). Apply it to your weapon and your next Attack deals an additional 6 damage of that element type. \\
	Remedy & 250G & Removes all negative status effects, except KO from a Close target.\\
	Malboro Vine & 250G & One Melee target makes a DC8 check and suffers Poison for 3r upon failure.\\
	%Sleep Powder & 250G & One Melee target makes a DC8 check and suffers Sleep for 3r upon failure.\\
	Hero Drink & 300G & One Close target gains EnSTR and EnMAG for 3r.\\
	%Warp Stone & 300G & You teleport to a place you can see within 10u.\\
	%Spider Web & 350G & The target makes a DC8 check and suffers Slow for 3 rounds upon failure.\\
	Hi-Potion & 400G & One Close target regains 20 HP. \\
	Scanner & 500G & Reveals one Melee target's Resiliences, Weaknesses, Immunities, current HP and MP.\\
	Turbo Ether & 500G & One Close target regains 30 MP. \\
	%Vaccine & 500G & Removes Poison and the target becomes Immune to it for the rest of the battle.\\
	%Megaphone & 500G & Removes Silence and the target becomes Immune to it for the rest of the battle.\\
	%Magic Lenses & 500G & Removes Blind and the target becomes Immune to it for the rest of the battle.\\
	%Pain Killer & 500G & Removes Immobile and the target becomes Immune to it for the rest of the battle.\\
	Phoenix Down & 500G & Removes KO and one restores 1 HP to a Close target.\\
	Tent & 500G & Allows the party to sleep outside comfortably. \\
	Dark Matter & 500G & One Melee target suffers 4d dark damage. \\
	X-Potion & 750G & One Close target fully regains their HP.\\
	%Transfusion & 800G & Removes Zombie and the target becomes Immune to it for the rest of the battle. \\ 
	%Silver Hourglass & 800G & Removes Slow and the target gains Haste for 3 rounds.\\
	Mega-Potion & 800G & All Close targets regains 25 HP.  \\
	%X-Ether & 900G & The target fully regains all MP.\\
	%Magicite Shard & 1000G & Roll 1d, based on the result use the following Esper Call: \newline 1-Ifrit, 2-Shiva, 3-Ramuh, 4-Odin, 5-Phoenix, 6-Bahamut.\\
	%Esper Magicite & 1250G & This Item is for one Esper (e.g. Ifrit Magicite). When used it activates its Call ability. \\
	Elixir & 1250G & One target fully regains their HP and MP. \\
	%Gold Hourglass & 1500G & Everyone within 5u except yourself suffers Sleep for 1 round. \\
	Mega-Elixir & 1750G & All Close targets fully regains their HP and MP.\\
	Mega-Phoenix & 2000G & Removes KO from all Close targets and fully restores their HP and MP.
}
%
]\twocolumn[
%
\oftablewide{p{0.3\columnwidth} p{0.05\columnwidth} p{0.125\columnwidth} p{1.475\columnwidth}}
{\oficonaccessory\accf{Accessory} & \accf{LV}& \accf{Value} & \accf{Effect}}
{
	 Mythril Shield & 1 & 500G & DEF +1  \\
	 Power Armlet & 1 & 500G & STR +1 \\
	 Rune Bracers & 1 & 500G & RES +1 \\
	 Crystal Ring & 1 & 500G & MAG +1 \\
	 %Battle Boots & 1 & Immunity: Immobile  \\
	 Silver Glasses & 1 & 500G & Immunity: Blind  \\
	 Star Pendant & 1 & 500G & Immunity: Poison  \\
	 White Cape & 1 & 500G & Immunity: Silence  \\
	 Berserker Badge & 1 & 500G & You gain EnSTR as long as your current MP is 5 or less. \\
	 Force Ring & 1 & 500G & You gain EnMAG as long as your MP is at its maximum.\\
	 %Ninja Tabi & 1 & Whenever you use the Dash action, you can move twice as far as usual.\\
	 Life Pendant & 1 & 500G & Whenever you recover from KO, you gain Regen for 3r. \\
	 %Utility Belt & 1 & You can use the Re-Equip action and still take another action.\\
	 %Buckler & 1 & Whenever you use the Defend action in combat, you also regain 3 HP.\\
	 Silent Boots & 4 & 1500G & Your footsteps are completely silent. \\
	 %Thief Gloves & 4 & You have Advantage on all checks related to stealing. \\
	 Protect Ring & 4 & 1500G & After being hit by an Attack, you gain EnDEF for 1r.\\
	 Fire Cufflink & 4 & 1500G & When you deal fire damage, add 3 to the amount. \\
	 Item Holder & 4 & 1500G & Choose an Item before combat. During, you can use it on top of an action.\\
	 Circlet & 4 & 1500G & RES +1, MAG +1\\
	 Grand Helmet & 4 & 1500G & STR +1, DEF +1\\
	 Safety Bit & 4 & 1500G & RES~+1, Immunity: KO \\ 
	 Champion Belt & 4 & 1500G & STR +1, Immunity: DeATR \\
	 Germinas Boots & 4 & 1500G & You can jump twice as high as usual.  \\
	 Black Belt & 4 & 1500G & Maximum HP +10  \\
     Heart Ring & 4 & 1500G & Maximum MP +10  \\
	 Moogle Charm & 4 & 1500G & Glows when there are monsters nearby.  \\
	 Muscle Belt & 8 & 3000G & When you roll 11 or higher on an Attack check, you score a Critical Hit. \\
 	 %Aegis Shield & 8 & Whenever you are targeted by Magic that does not involve a check already, you can try to pass a DC10 check to avoid its effect.\\
	 Hermes Shoes & 8 & 3000G & In every battle, you have Haste on your first turn. \\
	 Hero's Shield & 8 & 3000G & DEF +1, RES +1, Immunity: Sleep \\
	 Protect Bangle & 8 & 3000G & You gain EnDEF and EnRES as long as your HP is below 50\% of its maximum. \\
	 Feather Boots & 8 & 3000G & You can levitate up to 1u above the ground. \\
	 Hermes Sandals & 8 & 3000G & EVA~+1 \\
	 %Divine Sandals & 8 & You can walk on water and other liquids. \\
	 Genji Helmet & 8 & 3000G & RES~+2, DEF~+1.\\
	 Genji Shield & 8 & 3000G & DEF~+2, RES~+1.\\
	 Genji Gloves & 8 & 3000G & STR~+2, MAG~+2.\\
	 Rosetta Stone & 8 & 3000G & You are able to understand any written or spoken language. \\
	 Gold Hairpin & 8 & 3000G & The MP costs of all your abilities are reduced by 2.  \\
 	 Ribbon & 8 & 3000G & You gain advantage on all checks related to resisting Status Effects. \\
	 Godhand & 10 & ??? & Unique. When not wearing a weapon, you gain STR~+3 \& DEF~+3
	 %\multicolumn{3}{p{2\columnwidth}}{\hspace*{-0.15cm}\accf{Note:} For some accessories it does not make sense to wear two of the same kind (for example shields).}
}
%
\vspace*{0.5cm}\\
%
\oftablewide{p{0.25\columnwidth} p{0.125\columnwidth} p{1.63\columnwidth}}
{\accf{Materia} & \accf{Value} & \accf{Effect}}
{
	Water & 250G & Allows you to breathe normally under water. \\
	Conjuring & 250G & You can create simple magical effects, e.g. a loud noise or a flash of light.\\
	ATR Plus & 500G & This materia is of one the following attributes: STR, DEF, MAG or RES and increases the according attribute by 1 (e.g. STR Plus increases STR by 1).\\ 
	Resilience & 500G & This materia is of one elemental type (e.g. fire). You gain resilience against that type.\\
	Elemental & 500G & This materia is of one elemental type (e.g. fire). All your Attacks deal damage of this type.\\
	Immunity & 700G &  This materia is of one status effect (e.g. Blind) and grants Immunity against it.\\
	Status & 750G & This Materia is of one status effect (e.g. Poison). When you roll 9 or higher on an Attack check, the target additionally suffers it for 3r.\\
	Glow & 750G & The equipment infused piece glows in the dark to grant visibility nearby. \\
	Chocobo & 1000G & When you fall from any height, you can glide down gracefully. \\
	Signal & 1000G & You can use your action to shoot light into the air that is visible from large distances.\\ 
	HP Plus & 1250G & You maximum HP is increased by 10. \\
	MP Plus & 1250G & You maximum MP is increased by 10. \\
	Booster & 1250G & When you regain HP or MP from Items, the amount is doubled. \\ 
	Sense & 1500G & You can see the remaining HP of all enemies in Melee range. \\
	Mend & 1500G & You can use your action to remove one Status Effect that your are suffering. \\
	Vacuum & 2000G & You can use your action to pull an enemy from the back row to the front row. \\
	Exchange & 1750G & You can use your action to swap your position with an ally in the other row. \\
	Arcane & 1750G & You can detect the presence of nearby magically infused objects. \\
	Tough & 2000G & Whenever you make a check to withstand an effect, the DC is reduced by 1.\\
	X-Ray & 2000G & You can see through walls when standing next to them.\\
	Climb & 2500G & Allows you to walk on vertical surfaces the same as you can on the ground.\\
	Drain & 2500G & On every successful Attack, you regain 3 HP. \\
	Osmosis & 2500G & On every successful Attack, you regain 3 MP. \\
	Last Stand & 3000G & When your HP would drop to 0, it remains at 1. This effect can only be used once per combat.\\
	%Ghost & 3000G & Allows you to walk through people, monsters and solid objects that are not thinner than you.\\
	%Chameleon & 3000G & While not in combat, you can blend in with your environment. Enemies can only notice you by passing a DC9 check. \\ 
}
%
]
%
\clearpage
%
%