\ofchapterwithquote{Talent Skill List}{"Sweet Christmas, it’s a talking turtle!"}{Bartz}
%
\oftalent{Alchemist}
{
	After every battle against monsters you can create a Bomb Fragment or Lightning Gem from their remains. 
}
\vfill
\oftalent{Archylte Hunter}
{
	You have Advantage on all checks that require proficiency and experience related to nature, such as fishing or following tracks. 
}
\vfill
\oftalent{Blue Mage}
{
	You can quickly learn simple non-combat skills by carefully observing someone proficient. 
	Simple skills are for example cooking or fishing.
}
\vfill
\oftalent{Book Worm}
{
	You can understand the most important contents of any book or text in a matter of minutes.
}
\vfill
\oftalent{Camping, Again}
{
	While outside, you can spend an hour to build a comfortable shelter to spend the night out of materials found in nature.
}	
\vfill
\oftalent{Carpenter}
{
	Given enough time and materials, you can create and repair any object that is mostly made out of wood, such as furniture or vehicles.
}
\vfill
\oftalent{Chocobo Sage}
{
	You can comfortably tame and build friendships with friendly animals and monsters.
}
\vfill
\oftalent{Cid's Apprentice}
{
	Given enough time and materials you are able to repair any broken machine or vehicle. 
}
\vfill
\oftalent{Dedicated Driver}
{
	You are able to perfectly drive or navigate any vehicle including ships and airships. 
}
\vfill
\oftalent{Hope's Assistant} 
{
	Given any object or trace, you can determine its date and place of creation accurately.
}
\vfill
%
\oftalent{It's a Unix System}
{
	You can immediately understand electronic devices such as computer or communication systems.
}
%\vfill
%\oftalent{King's Shield}
%{
%	You have Advantage on all checks that rely on pure strength such as opening tight jar lids.
%}
\vfill
\oftalent{Leading Man}
{
	You have Advantage on all checks that involve impressing or persuading through speech. 
}
\newpage
\oftalent{Opera Floozy}
{
	You have Advantage on all checks that involve acting, singing, dancing or performing.
}
\vfill
\oftalent{Pyrotechnician} {
	Within an hour you can create an explosive from common materials.
	After a short setup, it can be used as distraction or to destroy small structures.
}
\vfill
\oftalent{Sceptic}
{
	You have Advantage on checks related to noticing whether someone is lying or withholding information.
}
\vfill
\oftalent{Shrouded One} 
{
	You have Advantage on all checks related to hiding or staying undetected.
}
\vfill
\oftalent{Simdemehkiym}
{
	You are fluent in 2 languages and can learn new ones in a matter of days.
}
\vfill
\oftalent{Spira's Historian}
{
	You have knowledge on most historical facts and you have Advantage on checks related to making connections to historical events. 	 
}
\vfill
\oftalent{Spoony Bard}
{
	You have perfectly mastered one music instrument of your choice and you can play other ones convincingly.
}
\vfill
\oftalent{Starplayer}
{
	You are among the best in the world in one sport or game of your choice.
}
\vfill
\oftalent{Strange Gourmand}
{
	You can spend an hour to prepare a tasty meal from almost anything that can be found in stores or in nature.
}
\vfill
\oftalent{Story Teller}
{
	You have Advantage on all checks related to telling convincing lies or omitting the truth.
}
\vfill
\oftalent{Tantalus Performer}
{
	You can use magic to create simple illusions, including voices and noises, small flames and gusts of wind.
}
\vfill
\oftalent{Theologian}
{
	You have perfect knowledge on all religions in the world, including their deities, customs and factions.
}
\vfill
\oftalent{Thief's Caution}
{
	You have Advantage on all checks related to noticing ambushes or hostile intentions of characters.
}
\vfill
\oftalent{Walkthrough}
{
	You have Advantage on all checks related to finding hidden locations and passages. 	 
}
\clearpage